From Archives to AI: A Dataset of Residential Property Listings in Brunei Darussalam

### 2024-12-15 analysis.qmd
Add relevant R files (#2) and edit cleanup script

---
title: Plots and data summaries for manuscript
author: Haziq Jamil
page-layout: full
grid:
  sidebar-width: 0px
editor_options: 
  chunk_output_type: console
html-table-processing: none
---

>>>>

---
title: Plots and Data Summaries
author: Haziq Jamil
page-layout: full
grid:
  sidebar-width: 0px
editor_options: 
  chunk_output_type: console
html-table-processing: none
---

### 2024-12-15 manuscript.qmd
Add relevant R files (#2) and edit cleanup script

---
title: House price data in Brunei
authors:
  - name: Haziq Jamil
    orcid: 0000-0003-3298-1010
    email: haziq.jamil@ubd.edu.bn
    url: "https://haziqj.ml"
    corresponding: true
    affiliations:
      - name: Universiti Brunei Darussalam
        id: ubd
        department: Mathematical Sciences, Faculty of Science
        address: Universiti Brunei Darussalam, Jalan Tungku Link
        city: Bandar Seri Begawan
        country: Brunei
        postal-code: BE 1410
  - name: Amira Barizah Noorosmawie
    affiliations:
      - ref: ubd        
  - name: Hafeezul Waezz Rabu
    affiliations:
      - ref: ubd
  - name: Lutfi Abdul Razak
    orcid: 0000-0003-1681-0895
    email: lutfi.razak@ubd.edu.bn
    affiliations:
      - ref: ubd              
date-modified: last-modified
abstract: |
  This article introduces the first publicly available dataset for analyzing the Brunei housing market, covering 31,495 property listings from 1993 to 2024. The dataset, curated from property advertisements in newspapers and online platforms, includes key attributes such as price, location, property type, and physical characteristics, enriched with area-level spatial information. Comprehensive and historical, it complements the Brunei Darussalam Central Bank’s Residential Property Price Index (RPPI), addressing the limitations of restricted access to raw RPPI data and its relatively short timeline since 2015. Data collection involved manual transcription from archival sources and automated web scraping using programmatic methods, supported by innovative cleaning with large language models (LLMs) to structure unformatted text. The dataset enables spatial and temporal analysis, with potential applications in economics, urban planning, and real estate research. While minor limitations exist, such as potential missing values and spatial coverage bias toward the Brunei-Muara district, this dataset provides a robust foundation for exploring housing market trends and informing policy decisions.
---

@@

Combining the workflow with a looping mechanism allowed for the systematic extraction of data from multiple pages and websites, and thus the automated scraping process enabled efficient data collection over time. 
This process however was highly contingent on the consistency of the structure of the websites being scraped from.
Over time, some websites shut down, while others changed their structure, requiring adjustments to the scraping scripts.
The web scraping process began in January 2022 and was conducted intermittently.
Data from 2012 up until the present (December 2024) were managed to be collected using this method, averaging around 1,500 listings per year.

@@

The primary goal was to extract the house characteristics of interest, specifically variables 7 to 15 as per @tbl-codebook, from the unstructured verbose descriptions scraped from property listing websites. 
Each description was processed with a carefully designed prompt (@fig-llm-prompt) to ensure consistent output. 
This prompt instructed the model to return only the required information in a semicolon-separated format, while handling edge cases such as missing descriptions, non-residential (commercial) properties, or rental property advertisements.

>>>>

---
title: "From Archives to AI: A Dataset of Residential Property Listings in Brunei Darussalam"
authors:
  - name: Haziq Jamil
    orcid: 0000-0003-3298-1010
    email: haziq.jamil@ubd.edu.bn
    url: "https://haziqj.ml"
    corresponding: true
    affiliations:
      - name: Universiti Brunei Darussalam
        id: ubd
        department: Mathematical Sciences, Faculty of Science
        address: Universiti Brunei Darussalam, Jalan Tungku Link
        city: Bandar Seri Begawan
        country: Brunei
        postal-code: BE 1410
  - name: Amira Barizah Noorosmawie
    affiliations:
      - ref: ubd        
  - name: Hafeezul Waezz Rabu
    affiliations:
      - ref: ubd
  - name: Lutfi Abdul Razak
    orcid: 0000-0003-1681-0895
    email: lutfi.razak@ubd.edu.bn
    affiliations:
      - ref: ubd              
date-modified: last-modified
abstract: |
  This article introduces the first publicly available dataset for analyzing the Brunei housing market, covering 31,495 property listings from 1993 to 2024. The dataset, curated from property advertisements in newspapers and online platforms, includes key attributes such as price, location, property type, and physical characteristics, enriched with area-level spatial information. Comprehensive and historical, it complements the Brunei Darussalam Central Bank’s Residential Property Price Index (RPPI), addressing the limitations of restricted access to raw RPPI data and its relatively short timeline since 2015. Data collection involved manual transcription from archival sources and automated web scraping using programmatic methods, supported by innovative cleaning with large language models (LLMs) to structure unformatted text. The dataset enables spatial and temporal analysis, with potential applications in economics, urban planning, and real estate research. While minor limitations exist, such as potential missing values and spatial coverage bias toward the Brunei-Muara district, this dataset provides a robust foundation for exploring housing market trends and informing policy decisions.
---

@@

Combining the workflow with a looping mechanism allowed for the systematic extraction of data from multiple pages and websites, and thus the automated scraping process enabled efficient data collection over time. REWORD / REMOVE
This process however was highly contingent on the consistency of the structure of the websites being scraped from.
Over time, some websites shut down, while others changed their structure, requiring adjustments to the scraping scripts.
[THAT'S WHY WE THOUGHT OF THE LLM THING...] 
The web scraping process began in January 2022 and was conducted intermittently.
Data from 2012 up until the present (December 2024) were managed to be collected using this method, averaging around 1,500 listings per year.

@@

The primary goal was to extract the house characteristics of interest, specifically variables 7 to 15 as per @tbl-codebook, from the unstructured verbose descriptions scraped from property listing websites. 
FOR THE REST OF THE VARIABLES, THIS CAN BE DONE SYSTEMATICALLY (e.g. dates and other metadata like agent name).
Each description was processed with a carefully designed prompt (@fig-llm-prompt) to ensure consistent output. 
This prompt instructed the model to return only the required information in a semicolon-separated format, while handling edge cases such as missing descriptions, non-residential (commercial) properties, or rental property advertisements.
